Quality Assesment of OpenStreetMap Footpath Data for 3D City Modelling

### 2020-05-12 report/report.tex
References in alphabetical order
Update todo
Correct Stojanovsky citing
Update SLU/OSM descriptions

The OSM project is based on Volunteered Geographical Information (VGI).
OSM road data and building footprints are commonly obtained by manually tracing features in commercially available satellite images.
Such images have a limit on their resolution which puts a theoretical limit on the accuracy of map features compared to their real-world equivalents (Haklay 2010).
Particularily the high resolution imagery from Bing in 2010 led to an increase in building information in OSM, and the positional error is largely due to the limited resolution in such satellite imagery. (Fan et al, 2014).

@@

The SLU map contains building features and property limits, but no road data.
The SLU map is maintained by The Swedish National Land Survey (Swedish: Lantmäteriet).
The SLU data is aqqcuired by land surveying methods such as GPS or DGNSS positioning, or by reproduction of features from ortophoto or stereo mapping from 3D aerial images.
The map is updated continously by Lantmäteriet, in conjoncture with the forming or reforming of property.
Building features in the SLU dataset have a position accuracy requirement of 2 meters.
(Lantmäteriet, 2019)

@@

@@

@@

\bibitem{stojanovski-20}
Stojanivski T. (2020). Viewpoint: City Information Modeling (CIM) And Digitizing Urban Design Practises. Article. Under review.

>>>>

The OSM project is a wiki-like geodatabase based on Volunteered Geographical Information (VGI), meaning anyone can contribute by adding or editing features.
OSM road data and building footprints are commonly obtained by manually tracing features in commercially available satellite images.
Such images have a limit on their resolution which puts a theoretical limit on the accuracy of map features compared to their real-world equivalents (Haklay 2010).
Particularily the high resolution imagery from Bing in 2010 led to an increase in building information in OSM, and the positional error is largely due to the limited resolution in such satellite imagery. (Fan et al, 2014).

@@

The SLU map is maintained by The Swedish National Land Survey (Swedish: Lantmäteriet).
The data is collected by geodetic professionals, by land surveying methods such as GPS or DGNSS positioning, or by reproduction of features from ortophoto or stereo mapping from 3D aerial images.
Building features in the SLU dataset have a position accuracy requirement of 2 meters.
The SLU map contains building features and property limits, but no road data.
The map is updated continously by Lantmäteriet, in conjoncture with the forming or reforming of property.
Whereas OSM is a free service, the SLU map is available to paying customers or for free to students and researchers.
(Lantmäteriet, 2019)

@@

% TODO: Move section 3.3 to preface (Exclude entirely?)
% TODO: Read through Todor's recommended papers

@@

\bibitem{stojanovski-20}
Stojanovski, T. Partanen J., Samuels I., Sanders, P. and Peters C. (2020, forthcoming). City Information Modelling (CIM) and Digitizing Urban Design Practices. Built Environment.

@@
